The {TestIdeals} package for \emph{Macaulay2}

### 2018-10-05 Fsing/TestIdealsPaper/TestIdeals.tex
Tiny change to paper.

\subsection{Parameter test modules}
%
%\pedro{Are we assuming here that $R$ is a quotient of a polynomial ring?}
%
Given an reduced ring $R$ of finite type over a perfect field $k$, the Frobenius map $R \hookrightarrow R^{1/p^e}$ is dual to $T : \omega_{R^{1/p^e}} \to \omega_R$.  As in \autoref{subsec.DualToFrobeniusOnQuotientRings}, we can represent the canonical module $\omega_R \subseteq R$ as an ideal, we can write $R = S/I$, and so we can find an element $u \in S^{1/p^e}$ representing the map $T:\omega_{R^{1/p^e}} \to \omega_R$; see \autoref{subsec.DualToFrobeniusOnQuotientRings} or \cite{KatzmanParameterTestIdealOfCMRings}.

>>>>

\subsection{Parameter test modules}
%
%\pedro{Are we assuming here that $R$ is a quotient of a polynomial ring?}
%
Given a reduced ring $R$ of finite type over a perfect field $k$, the Frobenius map $R \hookrightarrow R^{1/p^e}$ is dual to $T : \omega_{R^{1/p^e}} \to \omega_R$.  As in \autoref{subsec.DualToFrobeniusOnQuotientRings}, we can represent the canonical module $\omega_R \subseteq R$ as an ideal, we can write $R = S/I$, and so we can find an element $u \in S^{1/p^e}$ representing the map $T:\omega_{R^{1/p^e}} \to \omega_R$; see \autoref{subsec.DualToFrobeniusOnQuotientRings} or \cite{KatzmanParameterTestIdealOfCMRings}.
